Field-informed Reinforcement Learning for Learnining Large Scale Collective Tasks

### 2023-04-19 paper.tex
ref

In this paper, we propose a novel approach combining aggregate computing~\cite{Beal2015Computer} with Graph Neural Networks to focus on the relevant areas. We further combine this with reinforcement learning techniques to respond to changing conditions in the environment.
Specifically, we will show... \lukas{more info...}

>>>>

In this paper, we propose a novel approach combining aggregate computing~\cite{Beal2015Computer} with Graph Neural Networks~\cite{Zhou2020AIOpen} to focus on the relevant areas. We further combine this with reinforcement learning techniques to respond to changing conditions in the environment.
Specifically, we will show... \lukas{more info...}
